\documentclass[msc,numbers]{coppe}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{glossaries}

\makelosymbols{}
\makeloabbreviations{}

\newacronym[longplural={Internet Service Providers}]{isp}{ISP}{Internet Service
Provider}
\newacronym{ufrj}{UFRJ}{Federal University of Rio de Janeiro}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{docsis}{DOCSIS}{Data Over Cable Service Interface Specification}
\newacronym{cem}{CEM}{Crowdsourcing Event Monitoring}
\newacronym[longplural={Autonomous Systems}]{as}{AS}{Autonomous System}
\newacronym{bgp}{BGP}{Border Gateway Protocol}
\newacronym[longplural={Round Trip Times}]{rtt}{RTT}{Round Trip Time}
\newacronym[longplural={Content Delivery Networks}]{cdn}{CDN}{Content Delivery
Network}
\newacronym{snmp}{SNMP}{Simple Network Management Protocol}
\newacronym{udp}{UDP}{User Datagram Protocol}
\newacronym{vod}{VoD}{Video on Demand}
\newacronym{mse}{MSE}{Mean Squared Error}
\newacronym[longplural={Hidden Markov Models}]{hmm}{HMM}{Hidden Markov Model}
\newacronym{ip}{IP}{Internet Protocol}
\newacronym{tcp}{TCP}{Transmission Control Protocol}
\newacronym{hfc}{HFC}{Hybrid Fibre Coaxial}
\newacronym{qoe}{QoE}{Quality of Experience}
\newacronym{mpls}{MPLS}{Multi Protocol Label Switching}
\newacronym{nda}{NDA}{Non-Disclosure Agreement}
\newacronym[longplural={Cable Modem Termination Systems}]{cmts}{CMTS}{Cable Modem Termination System}

\begin{document}
    \title{Detection and Localization of Events in Computer Networks Using
    End-to-End Measurements Time Series}
    \foreigntitle{Detec\c{c}\~{a}o e Localiza\c{c}\~{a}o de Eventos em Redes de
    Computadores Utilizando S\'{e}ries Temporais de Medi\c{c}\~{o}es
    Fim-a-Fim.}
    \author{Diego Ximenes}{Mendes}
    \advisor{Prof.}{Edmundo Albuquerque de Souza e}{Silva}{Ph.D.}

    \examiner{Prof.}{Edmundo Albuquerque de Souza e Silva}{Ph.D.}
    \examiner{Prof.}{Antonio Jorge Gomes Abel\'em}{D.Sc.}
    \examiner{Prof.}{Daniel Sadoc Menasche}{Ph.D.}
    \examiner{Prof.}{Pedro Braconnot Velloso}{Dr.}
    \department{PESC}
    \date{10}{2017}

    \keyword{Time Series}
    \keyword{Change Point Detection}
    \keyword{Machine Learning}
    \keyword{Network Measurements}
    \keyword{Network Troubleshooting}

    \maketitle

    \frontmatter
    %\dedication{A algu\'em cujo valor \'e digno desta dedicat\'oria.}

    %\chapter*{Agradecimentos}

    \begin{abstract}
    \input{./src/resumo}
    \end{abstract}

    \selectlanguage{brazil}
    \begin{foreignabstract}
    \input{./src/abstract}
    \end{foreignabstract}

    \tableofcontents
    \listoffigures
    \listoftables
    \printlosymbols{}
    \printloabbreviations{}

    \mainmatter{}

    \input{./src/introduction}
    \input{./src/literature_review}
    \input{./src/change_point_detection}
    \input{./src/methodology}
    \input{./src/results}
    \input{./src/conclusion}

    \backmatter{}
    \nocite{*}
    \bibliographystyle{coppe-unsrt}
    \bibliography{./src/bibliography}

\end{document}
